Statistical Mechanics Informed Neural Networks for Solar Wind modeling

### 2024-12-10 paper/main.tex
default
paper

\begin{abstract}
    %TODO
\end{abstract}

@@

\begin{align*}
    \frac{\partial f_\alpha}{\partial t} + f_v \cdot \nabla_{\mathbf{r}} f_\alpha &+ \frac{q_\alpha ( f_E + f_v \times f_B)}{m_\alpha} \cdot \nabla_{\mathbf{v}} f_\alpha = 0 \text{ (Vlasov)}\\
    \sum_{\alpha} q_\alpha \int &f_\alpha d^3(f_v) = 0 \text{ (Quasineutrality)}\\
\frac{d}{dt} \int &f_\alpha \log f_\alpha d^3r d^3(f_v) = 0 \text{ (Liouville)}\\
\nabla \cdot f_E &= \frac{\sum_{\alpha} \rho_\alpha}{\epsilon_0} \\
\nabla \cdot f_B &= 0 \\
\nabla \times f_E &= - \frac{\partial f_B}{\partial t} \\
\nabla \times f_B &= \mu_0 \left(J + \epsilon_0 \frac{\partial f_E}{\partial t}\right) \text{ (Maxwell)} \\
\end{align*}

@@

\begin{align*}
    r &\in \left[10R_E, 240R_E\right] \\
    v_x &\in \left[300, 1000\right]\frac{km}{s} \\
    t &\in \left[0, 7200]s \\
\end{align*}

@@

\section{Methods}

\subsection{Neural Architecture Search (NAS)}
As an intermediate step before training, a hyperparameter grid search algorithm based in Bayesian multi-objective optimization is employed to find the neural architecture. The Pareto front is plotted, selecting minimization of neural complexity and loss function.

\section{Results}

\section{Discussion}

>>>>

\begin{abstract}
    Solar wind modeling presents significant challenges due to its complex, quasi-neutral, and collisionless plasma dynamics. Traditional magnetohydrodynamic (MHD) models often fail to accurately capture the system's intricate behavior. This research proposes a novel approach using Statistical Mechanics Informed Neural Networks to develop a more nuanced kinetic description of solar wind phenomena. By integrating Vlasov-Maxwell equations with physics-informed neural network architectures, we develop a computational framework that overcomes limitations of existing analytical and numerical models. The proposed methodology leverages data from space observatories including DSCOVR, ACE, and WIND, establishing boundary conditions from the L1-Lagrange point to Earth's orbit. Our approach directly embeds physical constraints into the neural network's learning process, enabling a more interpretable and computationally efficient model. The research demonstrates how physics-informed machine learning can provide insights into the complex dynamics of solar wind, moving beyond traditional temperature distributions and computational constraints.By combining statistical mechanics, kinetic theory, and advanced machine learning techniques, this work offers a promising new paradigm for understanding and predicting solar wind behavior, with potential implications for space weather prediction and fundamental plasma physics research.
\end{abstract}

@@

\begin{align*}
    \frac{\partial f_\alpha}{\partial t} + f_v \cdot \nabla_{\mathbf{r}} f_\alpha &+ \frac{q_\alpha ( f_E + f_v \times f_B)}{m_\alpha} \cdot \nabla_{\mathbf{v}} f_\alpha = 0 \text{ (Vlasov)}\\
\frac{d}{dt} \int &f_\alpha \log f_\alpha d^3r d^3(f_v) = 0 \text{ (Liouville)}\\
\nabla \cdot f_E &= 0 \text{ (Quasineutrality)}\\
\nabla \cdot f_B &= 0 \\
\nabla \times f_E &= - \frac{\partial f_B}{\partial t} \\
\end{align*}

@@

\begin{align*}
    r_x &\in \left[0, 230R_E\right] \\
    v_x &\in \left[0, 1000\right]\frac{km}{s} \\
    t &\in \left[0, 7200]s \\
\end{align*}

@@

\section{Results and discussion}

\subsection{1D-Simulations}

\subsection{2D-Simulations}
